%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}

\name{Muhammad}{Furqan}
\position{Senior Software Engineer{\enskip\cdotp\enskip}Hypervisor{\enskip\cdotp\enskip}Embedded Systems}
%\address{Lahore, Pakistan}

\mobile{+92 334 4347398}
\email{mfurqan1024@gmail.com}
%\dateofbirth{August 4th, 1998}
%\homepage{www.posquit0.com}
%\github{posquit0}
\linkedin{Furqan136}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

%\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Mr./Ms./Dr. LastName,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Muhammad Furqan~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a Senior Software Engineer with 3+ years of experience in <low-level> software development (Hypervisor)<, functional and unit testing>, and an academic and research background and interest in Machine Learning and Computer Vision. I am committed to delivering well-designed and maintainable codebase <Company/role goals><that enhances end user security>. My ability to quickly adapt to new projects and work collaboratively across teams ensures effective cross-functional collaboration.
\vspace{5pt}
\\
I am deeply passionate about Embedded software development due to the level of control and precision it offers. Its intricate nature challenges me to think critically, solve complex problems, optimize performance, and craft elegant solutions that can significantly impact the end-user experience. This constant drive for innovation is intellectually stimulating and creatively satisfying. <CV Interest> 

\lettersection{Why Google?}
<Company Inspiration><Apple's product design philosophy has always fascinated me with its seamless blend of elegance, simplicity, innovation, and an exceptional user experience. The prospect of contributing to this process drew me to pursue a career at Apple>. <Team/Work Interest><This position at Apple SPEAR stood out to me as it offers a unique blend of working on security in low-level systems and being part of a pioneering team. The opportunity to work on a brand new project at Apple is exciting and will allow me to make a meaningful impact in advancing the state of the art in end user security>. I am eager to contribute to the development of <company goals><secure and fortified systems>.

\lettersection{Why Me?}
I am working at Siemens DISW as a Senior Software Development Engineer on a C, C++ based Bare-Metal Hypervisor with support for x86 Virtualization, where I have enabled support for multiple versions of Windows, Linux, and multiple internal RTOSs. In this role, I enabled support for Intel Tigerlake-based Siemens SIMATIC 4x7G and Intel Atom Elkhartlake-based Siemens SIMATIC 2x7G systems, in collaboration with cross-functional international teams and ensured parallel development. I conducted Performance Optimization, Bugfixes, and Maintenance of various hypervisor components, including NVMe, PCIe, ACPI, AHCI, Timers, LAPIC, Trace Functionality, SIO, Boot/Reboot, MSR, CPUID, and Virtual BIOS (EDK). I have also designed and implemented Debian-based Installer with support for BTRFS. I have designed, developed, and automated various Test Scenarios for efficient Functional and Unit Testing. Additionally, I participated in training of new joiners and documentation of various designs, concepts, issues and codebase components.
\vspace{5pt}
\\
I have graduated with a Bachelor's degree in Computer Science with a CGPA of 3.49 / 4.0 (German 1.5/4.0). The degree included multiple courses related to <Embedded Systems and> System Programming<, Machine Learning and Computer Vision,> where I undertook various projects including Device Driver Development, <CV Projects> etc. During my time at the Information Technology University, I was awarded the Dean's' Honor List and a Full Academic Scholarship. Additionally, I was awarded a research position at the BiSMiL (\textit{Bio-Inspired Simulation of Machines and Intelligent Life}) Lab ITU in sophomore year <Where I worked on CV>.
\vspace{5pt}
\\
Aforementioned credentials and work experience in Embedded Systems<, Machine Learning and Computer Vision>, and my ability to deliver <robust solutions> makes me an ideal candidate to contribute to <Company>'s mission of <advancing end user security>. With my <technical expertise, collaborative approach, strong communication skills, and commitment to excellence>, I believe I will be a valuable asset to the <Team>.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
