%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Development Engineer} % Job title
    {SIEMENS DISW} % Organization
    {Lahore, Pakistan} % Location
    {Jan. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Successfully completed and delivered \textbf{multiple Multi-Million Euro projects}
        \item \textbf{Designed and Implemented} Debian based Installer for Hypervisor with support for BTRFS file system
        \item Enabled Hypervisor support for multiple versions of \textbf{Windows, Linux} and multiple internal \textbf{Real-Time Operating Systems}
        \item Conducted \textbf{Performance Optimization, Bugfixes and Maintenance} of various hypervisor components including Virtualization of NVMe, PCIe, ACPI, AHCI, Timers, LAPIC, Trace Functionality, SIO, Boot and Reboot Sequence, MSR, CPUID and Virtual UEFI BIOS (EDK)
        \item Enabled Support for \textbf{Intel Tigerlake} based Siemens SIMATIC 4x7G systems in \textbf{Collaboration with cross-functional international teams} and \textbf{ensured parallel development}
      \end{cvitems}
    }
    {C \acvSep C++ \acvSep Linux \acvSep RTOS \acvSep Virtualization}

%---------------------------------------------------------
  \cventry
    {Software Development Engineer} % Job title
    {} % Organization
    {} % Location
    {May. 2020 - Dec. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item \textbf{Enabled Support and Implemented} MSR and CPUID Virtualization for \textbf{Intel Atom} Elkhartlake based Siemens SIMATIC 2x7G series systems
        \item Conducted \textbf{Performance Optimization, Bugfixes and Maintenance} of various components including textbf{Virtualization} of NVMe, PCIe, Boot and Reboot Sequence, System Timers, ACPI Parser, Trace Functionality and Virtual UEFI BIOS
        \item \textbf{Designed, Developed and Automated} various Test Scenarios for efficient \textbf{Quality Assurance Testing}
      \end{cvitems}
    }
    {}%{C \acvSep C++ \acvSep Linux \acvSep RTOS \acvSep Virtualization}

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {MENTOR GRAPHICS} % Organization
    {Lahore, Pakistan} % Location
    {Jun. 2019 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Enabled support for Internal \textbf{Linux} Distributions on various \textbf{Arm }based systems
        \item Utilized \textbf{YOCTO} build system to customize and deploy Linux images for various Arm based devices
        \item Ported \textbf{Linux Kernel} updates and patches onto Internal Linux Distributions
        \item Adapted team and software \textbf{management systems and development processes} used in building and maintaining \textbf{large-scale software}
      \end{cvitems}
    }
    {C \acvSep C++ \acvSep Embedded Linux \acvSep YOCTO}

%---------------------------------------------------------
  \cventry
    {Research Intern} % Job title
    {BISMIL LAB - ITU} % Organization
    {Lahore, Pakistan} % Location
    {Jun. 2018 - Dec. 2018} % Date(s)
    {}
    {Python \acvSep MATLAB \acvSep Computer Vision}

    \cventry
    {Lab for Bio-Inspired Simulation of Machines and Intelligent Life} % Job title
    {} % Organization
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Collaborated with \textbf{Dr. Suleman Mazhar} on Cricket Shot Detection project
        \item \textbf{Awarded} under the Undergraduate Research Opportunities Program at ITU
        \item Being in early 4th semester, this was my introduction to \textbf{Academic Research} and to \textbf{AI, Machine Learning and Computer Vision}
      \end{cvitems}
    }
    {}

%---------------------------------------------------------
\end{cventries}
